---
title: "test_leaflet"
author: "JcB"
date: "14 mai 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

source: https://github.com/Robinlovelace/Creating-maps-in-R/blob/master/vignettes/leaflet-rstudio.Rmd

A first web map with leaflet
----------------------------
To create an interactive web map with leaflet is incredibly easy. Having installed the package try this single line of code:
```
# Plot a default web map (brackets display the result)
(m <- leaflet() %>% addTiles()) 
```

Adding basic features with %>%
------------------------------
Adding basic features to your webmap is easy. The %>% 'pipe' operator used extensively in dplyr and developed for the maggrittr package means we can finally escape from dozens of nested bracketted commands. (If you use RStudio, I suggest trying the new shortcut Ctl+Shift+M to produce this wonderful operator.) leaflet settings and functionality can thus be added sequentially, without requiring any additional brackets!

To add a location to the map m, for example, we can simply pipe m into the function setView():

m %>% setView(lng = -1.5, lat = 53.4, zoom = 10) # set centre and extent of map

This way we can gradually add elements to our map, one-by-one:
```
(m2 <- m %>%
  setView(-1.5, 53.4, 10) %>% # map location
  addMarkers(-1.4, 53.5) %>% # add a marker
  addPopups(-1.6, 53.3, popup = "Hello Sheffield!") %>% # popup
  # add som circles:
  addCircles(color = "black", runif(90, -2, -1), runif(90, 53, 54), runif(90, 10, 500)))
```

Application
-----------

```{r}
library(leaflet)

m <- leaflet() %>% addTiles()
m2 <- m %>% 
  setView(lng = 7.7455300, lat = 48.5839200, zoom = 10)  %>% # set centre and extent of map
  addMarkers(7.7455300, 48.5839200) %>% # add a marker
  addPopups(7.75, 48.6, popup = "Hello Strasbourg!") %>% # popup
  # add som circles:
  addCircles(color = "black", runif(90, 7, 8), runif(90, 48, 49), runif(90, 10, 500))

m2
```

Adding data
-----------
In the previous example, we added some random data that we created locally, inside the function call. How do we use real, large datasets in leaflet? The package provides 3 options:

    Data from base R: lat/long matrix or data.frame
    Data from sp such as SpatialPoints and SpatialPolygons
    Data from maps

Let's try adding a bicycle route, one that I followed with some friends to move from Sheffield to my current home of Leeds. First download some data:
```
url = "https://github.com/Robinlovelace/sdvwR/raw/master/data/gps-trace.gpx"
download.file(url, destfile = "shef2leeds.gpx", method = "wget")
```

__NOte__: provoque une erreur avec wget. Par contre fonctionne si on enlève wget:
```
download.file(url, destfile = "shef2leeds.gpx")
```

Now we can load this as a SpatialLinesDataFrame and display in leaflet:
```
library(rgdal)
shef2leeds <- readOGR("shef2leeds.gpx", layer = "tracks")
m2 %>%
  setView(-1.5, 53.4, 9) %>% # map location
  addPolylines(data = shef2leeds, color = "red", weight = 4)
```

Note in the above example that we had to use the argument data = to refer to our spatial object: it cannot simply be inserted without specifying what it is. The data argument can also be placed inside the initial leaflet() function call.